\textbf{Learning semi-Markovian DAGs with flow-based VAE}

### 2023-12-04 Tex/paper.tex
tex

Next, we juxtapose the performance of the two methods, each with varying proportions of bidirectional edges. The results, as illustrated in Figure \ref*{SHD_FDR_node10_20}, reveal that when the node size is 10, DAG-GNN surpasses our method in terms of SHD. However, when the node size is increased to 20, our method takes the lead, outperforming DAG-GNN in both SHD and FDR metrics.

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_10_DAG_threshold0.3.pdf}
        \caption{SHD with node size 10}
        \label{SHD_node10}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_10_DAG_threshold0.3.pdf}
        \caption{FDR with node size 10}
        \label{FDR_node10}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_20_DAG_threshold0.3.pdf}
        \caption{SHD with node size 20}
        \label{SHD_node20}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_20_DAG_threshold0.3.pdf}
        \caption{FDR with node size 20}
        \label{FDR_node20}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_30_DAG_threshold0.3.pdf}
        \caption{SHD with node size 30}
        \label{SHD_node30}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_30_DAG_threshold0.3.pdf}
        \caption{FDR with node size 30}
        \label{FDR_node30}
    \end{subfigure}
    \caption{SHD and FDR with dependence proportion 0.1, 0.3, 0.5, and 0.8}
    \label{SHD_FDR_node10_20}
\end{figure}

For the number of predicted edges, we observe that our method produces a number of edges closer to the true number of edges than DAG-GNN, especially when the node size is 20. As shown in Figure \ref*{pred_edge}, the number of predicted edges from both methods are similar when the node size is 10. However, when the node size is 20, our method produces a number of predicted edges closer to the true number of edges than DAG-GNN. Considering that our method outperforms DAG-GNN in terms of SHD and FDR, we can conclude that our method produces a more accurate graph structure than DAG-GNN.

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_10_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 10}
        \label{pred_edge_node10}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_20_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 20}
        \label{pred_edge_node20}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_30_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 30}
        \label{pred_edge_node30}
    \end{subfigure}
    \caption{Number of predicted edges with dependence proportion 0.1, 0.3, 0.5, and 0.8}
    \label{pred_edge}
\end{figure}

>>>>

Next, we compare the performance of the two methods, each with varying proportions of bidirectional edges. The results, as illustrated in Figure \ref*{SHD_FDR}, reveal that when the node size is 10, DAG-GNN surpasses our method in terms of SHD. However, when the node size is increased to 20, our method takes the lead, outperforming DAG-GNN in both SHD and FDR metrics.

\begin{figure}
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_10_DAG_threshold0.3.pdf}
        \caption{SHD with node size 10}
        \label{SHD_node10}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_10_DAG_threshold0.3.pdf}
        \caption{FDR with node size 10}
        \label{FDR_node10}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_20_DAG_threshold0.3.pdf}
        \caption{SHD with node size 20}
        \label{SHD_node20}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_20_DAG_threshold0.3.pdf}
        \caption{FDR with node size 20}
        \label{FDR_node20}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_30_DAG_threshold0.3.pdf}
        \caption{SHD with node size 30}
        \label{SHD_node30}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_30_DAG_threshold0.3.pdf}
        \caption{FDR with node size 30}
        \label{FDR_node30}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_50_DAG_threshold0.3.pdf}
        \caption{SHD with node size 50}
        \label{SHD_node50}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_50_DAG_threshold0.3.pdf}
        \caption{FDR with node size 50}
        \label{FDR_node50}
    \end{subfigure}
    \caption{SHD and FDR with dependence proportion 0.1, 0.3, 0.5, and 0.8}
    \label{SHD_FDR}
\end{figure}

In terms of the number of predicted edges, we observe that our method produces a number of edges closer to the true number of edges than DAG-GNN, especially when the node size is 20. As shown in Figure \ref*{pred_edge}, the number of predicted edges from both methods are similar when the node size is 10. However, when the node size is 20, 30 and 50, our method produces a number of predicted edges closer to the true number of edges than DAG-GNN. Considering that our method outperforms DAG-GNN in terms of SHD and FDR, we can conclude that our method produces a more accurate graph structure than DAG-GNN.

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_10_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 10}
        \label{pred_edge_node10}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_20_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 20}
        \label{pred_edge_node20}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_30_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 30}
        \label{pred_edge_node30}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_50_DAG_threshold0.3.pdf}
        \caption{Predicted edges with node size 50}
        \label{pred_edge_node50}
    \end{subfigure}
    \caption{Number of predicted edges with dependence proportion 0.1, 0.3, 0.5, and 0.8}
    \label{pred_edge}
\end{figure}
